Reduced GW invariants from cuspidal curves

### 2018-01-10 draft_merged.tex
finished reviewing loc vir pb commutes with pf

\[\mathfrak{C}_{Y'/S'}\subseteq \varphi'^* \mathfrak{C}_{Y/S}\subseteq \mathbb E_{Y'/S'}(\sigma')\]

@@

The above construction applies to $\Z^p$.
Indeed consider on $\Z^p$ the perfect obstruction theory: \[\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic}_1{(1)}}\right)\] and the induced cosection
$\alpha^*\sigma\colon \OO b_{\Z^p/\XP}\to \Z^p$
with degeneracy locus:
\[\pazocal D(\alpha^*\sigma)=\Mone{1}{X}{d}\times_{\Mone{1}{\PP^4}{d}^p} \Z^p.\]
Then we have that
\begin{align*}
\mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1}{(1)}}\\
& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)(\sigma)\\
&\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)(\alpha^*\sigma)
\end{align*}
and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}:=\gamma^!_{\mathbb E_{\Z^p/\XP},\alpha^*\sigma}[\XP].$
\begin{lem}\label{lem:comutativity}
With the same setup and notation as in the definition of localised virtual pullback, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$. then
for any $[B']\in A_*(\varphi'^*\mathbb{E}(\sigma'))$
\begin{equation}\label{eq:commcos}\varphi'_*( s^!_{\sigma',\rm{loc}}[B'])=s^!_{\sigma,\rm{loc}}\left(\varphi^{\mathbb{E}}_*[B']\right)\,\in\, A_*(Y(\sigma)) 
\end{equation}
where $\varphi^{\mathbb{E}}\colon \varphi'^*\mathbb{E}(\sigma')\to \mathbb{E}(\sigma)$ is the natural induced morphism.
\end{lem}
\begin{proof}
If $B'\subset \mathbb{E}\rvert_{Y'(\sigma')}$ then $\varphi(\sigma)(B')\subset \mathbb{E}\rvert_{Y(\sigma)}$
thus the localised Gysin morphism are just $s^!_{\mathbb{E}\rvert_{Y'(\sigma')}}$, $s^!_{\mathbb{E}\rvert_{Y(\sigma)}}$ and the fact they commute with proper push-forward is already well known, see \cite{Kresh} or simply \cite[Chapter~4]{Fulton} if we assume the existence of global resolutions.

Let now $B'$ be a (integral) cycle in $\mathbb{E}(\sigma')$ not contained in  the restriction of the vector bundle stack to the degeneracy locus of $\sigma'.$ Then, accordingly to the construction recalled at the beginning of this section, 
 \[s^!_{\sigma',\rm{loc}}[B']:=k^{-1} \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y'(\sigma')).\]
 where $\nu'\colon X\to Y'$ and $\nu'*\sigma'$ satisfy conditions~\eqref{cond:deflocal}. Notice that if we consider the composition
 $\nu\colon X\xrightarrow{\nu'} Y'\xrightarrow{\varphi} Y$ and the pull-back $\nu^*\sigma,$ the first two conditions in \eqref{cond:deflocal} are satisfied for any $B\in A_*(\mathbb E(\sigma)).$ 
 Consider 
 \[\widetilde{B}\to B'\to \varphi^{\mathbb{E}}(B'):=B.\]
 Suppose first that $B'\to B$ is generically finite of degree $h$, then $\widetilde{B}\to B$ satisfy the last condition in \eqref{cond:deflocal} and
 \begin{align*}
 \varphi'_*( s^!_{\sigma',\rm{loc}}[B'])&= k^{-1}\varphi'_*\ \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
 &=k^{-1} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
 &=h\, s_{\sigma,\rm{loc}}^![B]\\
 &=s_{\sigma,\rm{loc}}^!(\varphi^{\mathbb{E}}_*[B'])
 \end{align*}
If instead $B'\to B$ is not generically finite, then the RHS  in \eqref{eq:commcos} is zero. Let us show that the same is true for the LHS. By \cite[Lemma~2.7]{KLcosection}, to show that 
\[\operatorname{LHS}=\nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)=0\,\in A_*(Y(\sigma)),\]
with $[\widetilde{B}]\in \, Z_*(G),$
it is enough to show that $\nu_*^{\mathbb{E}}[\widetilde B]$ is zero in $A_*(\mathbb{E})$ where $\nu^{\mathbb{E}}$ is the natural morphism induced by $\nu.$ Then it is immediate, indeed since  $\nu^{\mathbb{E}}=\varphi^{\mathbb{E}}\circ\nu'^{\mathbb{E}}$  and we assumed $\varphi^{\mathbb{E}}\colon B'\to B$ has fibers of positive dimension, $\nu_*^{\mathbb{E}}[\widetilde B]=0$ by definition of proper push-forward.

\begin{cor}
$\deg[\Z^p]^{\rm{vir}}_{\rm{loc}}=\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}$
\end{cor}
\begin{proof}
We show that
\[\alpha_*[\Z^p]^{\alpha^*\sigma_1,\rm{vir}}_{\rm{loc}}=[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\sigma_1,\rm{loc}},\]
then the statement follow given that $\alpha$ is generically 1 to 1.
Notice  first of all that the 1-stabilisation $\mathfrak{M}_1^{\rm{w}}\to \mathfrak{M}_1^{1,\rm{w}}$ is proper. As usual, we use the lifting criterion and thus we have to show that, up to a base change, the dashed arrow and the $\mathcal C$ in the following commutative diagram exist
\bcd
\mathcal C_{\eta}\ar[d,"\phi_{\eta}"] \ar[r,dashed, hookrightarrow] &\mathcal C\ar[d, dashed, "\phi"]\\
\hat{\mathcal C_{\eta}}\ar[r, hookrightarrow] &\hat{\mathcal{C}}
\ecd
where the family are over a DVR $T$ and $\eta$ is its generic point. We can in fact assume that $\phi_{\eta}$ is an isomorphism and then notice that it is enough to consider the semi-stable model of $\hat{\mathcal C}.$
Thus, since the 1-stabilisation $\phi$ is generically an isomorphism it follows that
\[\phi_*[\mathfrak{M}_1^{\rm{w}}]=[\mathfrak{M}_1^{1,\rm{w}}]\]
and analogously,
\[\phi_*[\XP]=[\mathfrak{Pic_1{(1)}}]\]
Finally, recall that the deformation to the normal cone construction ensures the commutativity of
\bcd
A_*(\XP)\ar[r,"\zeta'"]\ar[d,"\phi_*"] & A_*(\mathfrak C_{\Z^p/\XP}) \ar[d,"\phi(\sigma)_*"]\\
A_*(\mathfrak{Pic_1{(1)}})\ar[r,"\zeta"] & A_*(\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}})
\ecd
and thus 
\[\phi(\sigma)_*[\mathfrak C_{\Z^p/\XP}]\cong [\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}].\]
The identity at the level of virtual classes now follows from the definition of cosection localised virtual class and Lemma~\ref{lem:comutativity}.
\end{proof}

>>>>

\[\mathfrak{C}_{Y'/S'}\subseteq (\varphi')^* \mathfrak{C}_{Y/S}\subseteq \mathbb E_{Y'/S'}(\sigma')\]

@@

The above construction applies to $\Z^p$.
Indeed consider on $\Z^p$ the perfect obstruction theory: \[\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic}_1{(1)}}\right)\] and the induced cosection
$\alpha^*\sigma\colon \OO b_{\Z^p/\XP}\to \Z^p$
with degeneracy locus:
\[\pazocal D(\alpha^*\sigma)=\Mone{1}{X}{d}\times_{\Mone{1}{\PP^4}{d}^p} \Z^p.\]
Then we have that
\begin{align*}
\mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1}{(1)}}\\
& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic}_1{(1)}}\right)(\sigma)\\
&\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)(\alpha^*\sigma)
\end{align*}
and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}:=\gamma^!_{\mathbb E_{\Z^p/\XP},\alpha^*\sigma}[\XP].$
\begin{lem}\label{lem:comutativity}
With the same setup and notation as in the definition of localised virtual pullback, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$. For every cycle $[B']\in A_*(S')$,
\[\phi'_*\circ(\rho')^!_{\mathbb E_{Y'/S'}}[B']=(\rho)^!_{\mathbb E_{Y/S}}\circ\phi_*[B]\in A_*(Y(\sigma)).\]

\end{lem}
\begin{proof}
Consider the following diagram:
\bcd
A_*(S')\ar[r]\ar[d] & A_*(\mathfrak C_{Y'/S'}) \ar[r]\ar[d] & A_*(h^1/h^0(\mathbb E_{Y'/S'})(\sigma'))\ar[r,"s_{\sigma',\rm{loc}}^!"]\ar[d] & A_*(Y'(\sigma'))\ar[d] \\
A_*(S)\ar[r] & A_*(\mathfrak C_{Y/S}) \ar[r] & A_*(h^1/h^0(\mathbb E_{Y/S})(\sigma))\ar[r,"s_{\sigma,\rm{loc}}^!"] & A_*(Y(\sigma))
\ecd
Only the left-most square is not classical. Hence we are left with showing that for every cycle $[B']\in A_*(h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma'))$ we have:
\begin{equation}\label{eq:commcos}\varphi'_*( s^!_{\sigma',\rm{loc}}[B'])=s^!_{\sigma,\rm{loc}}\left(\varphi^{\mathbb{E}}_*[B']\right)\,\in\, A_*(Y(\sigma)),
\end{equation}
where $\varphi^{\mathbb{E}}\colon h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma')\to h^1/h^0(\mathbb{E}_{Y/S})(\sigma)$ is induced by the morphism of vector bundle stacks.

If $B'\subset h^1/h^0(\mathbb{E}_{Y'/S'})\rvert_{Y'(\sigma')}$ then $\varphi^{\mathbb E}(B')\subset h^1/h^0(\mathbb{E}_{Y/S})\rvert_{Y(\sigma)}$,
thus the localised Gysin morphisms coincide with $s^!_{h^1/h^0(\mathbb{E}_{Y'/S'})\rvert_{Y'(\sigma')}}$ and $s^!_{h^1/h^0(\mathbb{E}_{Y/S})\rvert_{Y(\sigma)}}$, and their commutativity with proper pushforward is well-known, see \cite{Kresch} (or \cite[Chapter~3]{FUL} if we assume the existence of global resolutions).

Assume then that $B'$ is a prime cycle in $h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma')$ not contained in $h^1/h^0(\mathbb{E}_{Y'/S'})\rvert_{Y'(\sigma')}$. Then, according to the construction recalled at the beginning of this section, 
 \[s^!_{\sigma',\rm{loc}}[B']:=\frac{1}{k} \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y'(\sigma')),\]
 where $\nu'\colon X\to Y'$, $(\nu')^*(\sigma')$ and $\widetilde B$ satisfy the conditions~\eqref{cond:deflocal}. Notice that if we consider the composition
 $\nu\colon X\xrightarrow{\nu'} Y'\xrightarrow{\varphi'} Y$ and the pull-back $\nu^*(\sigma)$, the first two conditions in \eqref{cond:deflocal} are satisfied. How about
 \[\widetilde{B}\to B'\to \varphi^{\mathbb{E}}(B')=:B?\]
 Suppose first that $B'\to B$ is generically finite of degree $h$; then $\widetilde{B}\to B$ satisfies the last condition in \eqref{cond:deflocal} and has degree $hk$, so:
 \begin{align*}
 \varphi'_*( s^!_{\sigma',\rm{loc}}[B'])&= \frac{1}{k}\varphi'_*\ \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
 &=\frac{1}{k} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
 &=h\, s_{\sigma,\rm{loc}}^![B]\\
 &=s_{\sigma,\rm{loc}}^!(\varphi^{\mathbb{E}}_*[B']).
 \end{align*}
If instead $B'\to B$ is not generically finite, then the right-hand side in formula \eqref{eq:commcos} is zero. In order to show that the same is true for the left-hand side it is enough to appeal to \cite[Lemma~2.7]{KLcosection}, since $\nu_*^{\mathbb{E}}[\widetilde B]=(\nu')_*^{\mathbb E}\circ \phi^{\mathbb E}_*[\widetilde B]=0.$ %to show that 
%\[\operatorname{LHS}=\nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)=0\,\in A_*(Y(\sigma)),\]
%with $[\widetilde{B}]\in \, Z_*(G),$
%it is enough to show that $\nu_*^{\mathbb{E}}[\widetilde B]$ is zero in $A_*(\mathbb{E})$ where $\nu^{\mathbb{E}}$ is the natural morphism induced by $\nu.$ Then it is immediate, indeed since  $\nu^{\mathbb{E}}=\varphi^{\mathbb{E}}\circ\nu'^{\mathbb{E}}$  and we assumed $\varphi^{\mathbb{E}}\colon B'\to B$ has fibers of positive dimension, $\nu_*^{\mathbb{E}}[\widetilde B]=0$ by definition of proper push-forward.
\end{proof}

\begin{cor}
$\deg[\Z^p]^{\rm{vir}}_{\rm{loc}}=\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}$
\end{cor}

This descends from the following lemma and the fact that $\XP$ and $\mathfrak{Pic}_1(1)$ are birational.

\begin{lem}
 The $1$-stabilisation $\mathfrak{M}_1^{\rm{wt,st}}\to \mathfrak{M}_1^{\rm{wt,st}}(1)$ is a proper morphism.
\end{lem}
\begin{proof}
Use the valuative criterion: let $\dvr$ be a DVR scheme with generic point $\eta$; we have to fill in the upper right part of the following diagram:
\bcd
\mathcal C_{\eta}\ar[d,"\phi_{\eta}"] \ar[r,dashed, hookrightarrow] &\mathcal C\ar[d, dashed, "\phi"]\\
\hC_{\eta}\ar[r, hookrightarrow] &\hC
\ecd
We may in fact assume that $\phi_{\eta}$ is an isomorphism, and then it is enough to take the semistable model of $\hC.$
\end{proof}
%We show that
%\[\alpha_*[\Z^p]^{\alpha^*\sigma_1,\rm{vir}}_{\rm{loc}}=[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\sigma_1,\rm{loc}},\]
%then the statement follow given that $\alpha$ is generically 1 to 1.
%Notice  first of all that  As usual, we use the lifting criterion and thus we have to show that, up to a base change, the dashed arrow and the $\mathcal C$ in the following commutative diagram exist

%where the family are over a DVR $T$ and $\eta$ is its generic point. We can in fact assume that $\phi_{\eta}$ is an isomorphism and then notice that it is enough to consider the semi-stable model of $\hat{\mathcal C}.$
%Thus, since the 1-stabilisation $\phi$ is generically an isomorphism it follows that
%\[\phi_*[\mathfrak{M}_1^{\rm{w}}]=[\mathfrak{M}_1^{1,\rm{w}}]\]
%and analogously,
%\[\phi_*[\XP]=[\mathfrak{Pic_1{(1)}}]\]
%Finally, recall that the deformation to the normal cone construction ensures the commutativity of
%\bcd
%A_*(\XP)\ar[r,"\zeta'"]\ar[d,"\phi_*"] & A_*(\mathfrak C_{\Z^p/\XP}) \ar[d,"\phi(\sigma)_*"]\\
%A_*(\mathfrak{Pic_1{(1)}})\ar[r,"\zeta"] & A_*(\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}})
%\ecd
%and thus 
%\[\phi(\sigma)_*[\mathfrak C_{\Z^p/\XP}]\cong [\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}].\]
%The identity at the level of virtual classes now follows from the definition of cosection localised virtual class and %Lemma~\ref{lem:comutativity}.
%\end{proof}
